\begin{abstract}
	Firstly, I would like to express my very great appreciation to my supervisor, Partha S. Roop. 
	He expended a lot of time and a lot of effort to get me to the point where I am now, and I am exceedingly grateful for that.
	He guided me through the tenure of my thesis, showing me what needed to be done, but not doing it for me.
	I learned many new and interesting concepts and technologies while working with him and was able to produce a great thesis with original work.
	
	Secondly, Hammond Pearce has my utmost thanks.
	He took the role as a secondary supervisor to me, even with his own work as a PhD student.
	He helped me many a time when I was stuck, had a question or needed a push in the right direction.
	We spent many hours covering my current line of work and getting me back on line.
	
	Next is the research group with Partha Roop. 
	Many thanks to Matthew Kuo, Nathan Allen and Jin Ro.
	All three gentlemen helped me numerous times during my time as a ME student.
	
	A thanks to Yash Raje, who was a great lab and Master's partner, and someone I spent a lot of time working with.
	
	Without Marc Katzef, University of Canterbury, I would not have been able to use the extremely well made MNN2C tool.
	He did a really great job creating it in his time spent at the University of Auckland, and I would like to thank him for his fantastic work.
	
	Finally, I wish to thank my family; my mom Lynette, my dad Ara, my stepmom Sara, my aunt Mona, my brothers Damian and Liam, and last, but not least, a friend of many years, Alex. 
	They all supported me throughout this degree and gave me the love and encouragement I needed.
	
\end{abstract}