\section{Artificial Neural Networks}
\subsection{Machine Learning}
What is machine learning. Where is it used. Some examples.

\subsection{Efficacy of Machine Learning}
How does machine learning (ANNs) improve systems these days?

\subsection{Structure of an Artificial Neural Network}
How does an ANN run, how does it train, what does it look like.

\subsection{Safety of Artificial Neural Networks}
Safety drawbacks of ANNs:
Unpredictable
Hard to verify
Slow
Etc


\section{Synchronous Languages}
\subsection{Synchronous Semantics}
Briefly explain synchronous semantics: what is synchronous programming and how does it work?

\subsection{Safety of Synchronous Languages}
What guarantees does synchronous programming provide?
Determinism
Causality
Easy to formalise
Etc

\subsection{Timing Correctness}
Time predictability.

\subsection{Functional Correctness}
Runtime Enforcement


\section{Time Predictable Cyber-Physical Systems}
\subsection{Worst Case Execution Time}
Explain what WCET is in safety critical systems. Why is it important for deadlines to be met and how does this relate to WCET?

\subsection{Worst Case Reaction Time}
WCRT vs WCET. Throughput vs Time.

\subsection{Timing Techniques}
What timing techniques exist for synchronous and asynchronous systems? Which of these are relevant to our work?

\subsection{Patmos Time Predictable Processor}
Brief description of Patmos and why we use it.


\section{Verification of Artificial Neural Networks}
This section looks into ANN verification methods and why they are good/bad.

\subsection{The Problem of Artificial Neural Network Verification}
ANN verification is an issue. Why?

\subsection{Existing Techniques for Verifying ANNs}
Rundown of existing techniques of ANN verification.

\subsection{Limitations of Artificial Neural Network Verification}
Describe where verification is limited and why.
Where can it do better?


\section{Run-time Enforcement}
\subsection{Run-time Assurance}
What is RA and why is it useful? Formally defined.

\subsection{Run-time Monitoring}
How does this relate and improve on RA?

\subsection{Run-time Enforcement}
Benefits? Synchronous vs asynchronous systems. 

\subsection{Safety (Timed) Automata}
These are used in our run-time enforcement techniques. Discuss these and how they work.

\section{Summary}
Summary of above.